\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\PROJECT TETRIS}

\author{Team \#11, Team Tetra
		\\ Daniel Agostinho agostd
		\\ Anthony Chang changa7
		\\ Divya Sridhar sridhad
}

\date{}


\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 23, 2016 & Daniel Agostinho & Initial Draft\\
September 23, 2016 & Anthony Chang & Initial Draft\\
September 23, 2016 & Divya Sridhar & Initial Draft\\
December 4, 2016 & Daniel Agostinho & Revision 1\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

\section{Problem Statement}

\subsection{The Problem}
Many people feel the need to escape their crazy, work-filled lives for a few moments and just enjoy themselves in an easy and stimulating way. They search for a means to challenge themselves and feel a real sense of accomplishment. However, these people need something simple enough to learn quickly and they need it to be easily accessible. Many people turn to video games to solve this problem as they are fun, easy and fulfill our innate human desire to play. There are many games only available on the mobile phone platform but this limits the accessibility of these games to only those with a smartphone.
\subsection{The Importance}
Playing games of any kind is an important tool in relieving stress and stimulating the minds of the stakeholders. It allows them to temporarily disburden themselves from the responsibilities of the real world and allow them to express creativity. Regardless of who the stakeholder is, stimulating the mind and encouraging creativity has benefits that can improve all other aspects of their lives.
\subsection{The Context}
The stakeholders of this software are not limited to one specific set of people. Anyone of any age can enjoy Project Tetris. Project Tetris is a game that will be available to anyone that can run Java regardless of the operating system used (Windows, Mac OS, or Linux). For example, this allows a stakeholder in an office setting easy access to this software.

\end{document}