\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Proof of Concept Plan\\PROJECT TETRIS}

\author{Team Tetris, Team Name
		\\ Daniel Agostinho agostd
		\\ Anthony Chang changa7
		\\ Divya Sridhar sridhad
}

\date{}

\input{../Comments}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Date1 & Name(s) & Description of changes\\
Date2 & Name(s) & Description of changes\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

Put your problem statement here.

\section{Challenges & Risks}
\subsection{Most Significant Risk}
The most significant risk will be subdividing the tasks among group members and working simultaneously. With the scale of the project being so small, dividing the work will be difficult. Each potential subtask will not be specific enough to do individually. To overcome this risk, Team Tetris is going to break down the total project into the MVC structure and work on each component together. For each component, the team will communicate regularly while coding and commit their changes to the code sequentially such that each member can build off of what previous members have committed in their code. Team Tetris will demonstrate the working game logic for PROJECT TETRIS to show how the risk was overcome. 
\subsection{Will a part of the implementation be difficult?}
The most difficult part of the implementation will be designing the game while conforming to the MVC structure. It would be much simpler to create this program in one class, but in order for the software to be good, it must follow certain principles such as low coupling and high cohesion. 
\subsection{Will testing be difficult?}
Testing will not be difficult due to the group members' experience in JUnit Testing.
\subsection{Is a required library difficult to install?}
There will not be any libraries involved that will be difficult to install. Most of the libraries will come from java.awt or java.util.
\subsection{Will portability be a concern?}
Portability will not be a concern because the game is Java based. Most computers run Java/ are available to run Java. The only constraint on the user is that they have an internet connection to download the game. Across operating systems, portability is still not a concern since the game can be run on Windows, OS X, and Linux.


\end{document}