\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts


\title{SE 3XA3: Problem Statement}
\title{Project: Tetris}
\author{Group 11}
\date{September 23, 2016}							% Activate to display a given date or no date

\begin{document}
\maketitle


%page 2 with table of contents
\newpage
\tableofcontents
\section{Revision History}
\begin{table}[h!]
  \centering
  \caption{Table 1: Revision History: Proof of Concept and Problem Statement}
  \label{tab:table1}
  \begin{tabular}{cccc}
    Date & Developer & Change & Revision\\
    \hline
    September 23, 2016 & Daniel Agostinho & Initial Draft & 0\\
    \hline
    September 23, 2016 & Anthony Chang & Initial Draft & 0\\
    \hline
    September 23, 2016 & Divya Sridhar & Initial Draft & 0\\

  \end{tabular}
\end{table}


\section{Problem Statement}

\subsection{The Problem?}
Many people feel the need to escape their crazy, work-filled lives for a few moments and just enjoy themselves in an easy and stimulating way. They search for a means to challenge themselves and feel a real sense of accomplishment. However, these people need something simple enough to learn quickly and they need it to be easy accessible. Many people turn to video games to solve this problem as they are fun, easy and fulfill our innate human desire to play. There are many games only available on the mobile phone platform but this limits the accessibility of these games to only those with a smartphone.
\subsection{The Importance?}
Playing games of any kind is an important tool in relieving stress and stimulating the minds of the stakeholders. It allows them to temporarily disburden themselves from the responsibilities of the real world and allow them to express creativity. Regardless of who the stakeholder is, stimulating the mind and encouraging creativity has benefits that can improve all other aspects of their lives.
\subsection{The Context?}
The stakeholders of this software are not limited to one specific set of people. Anyone of any age can enjoy Project Tetris. Project Tetris is a game that will be available to anyone that can run Java regardless of the operating system used (Windows, Mac OS, or Linux). For example, this allows a stakeholder in an office setting easy access to this software.


\end{document}  